Forecasting 2024 US election using linear regression

### 2024-10-25 paper/paper.qmd
update the appendix

In addition to constructing and interpreting predictive models, this paper dive into the methods used by xx pollsters, analyzing the strengths as well as the weaknesses of the methods used against them. At the end of the paper, we also propose an idealized survey methodology for election forecasting with a budget of $100,000 USD.

@@

\begin{align} 
vote\_harris_i|\pi_i &\sim \text{Bernoulli}(\pi_i) \\
\text{logit}(\pi_i) &= \beta_0 + \beta_1 \text{sex}_i + \beta_2  \text{age\_bracket}_i + \beta_3 \text{race}_i + \beta_4 \text{race\_hispanic}_i + \beta_5 \text{education\_level}_i + \beta_6 \text{urban}_i \\
\beta_0 &\sim \text{Normal}(0, 2.5) \\
\beta_1 &\sim \text{Normal}(0, 2.5) \\
\beta_2 &\sim \text{Normal}(0, 2.5) \\
\beta_3 &\sim \text{Normal}(0, 2.5) \\
\beta_4 &\sim \text{Normal}(0, 2.5) \\
\beta_5 &\sim \text{Normal}(0, 2.5) \\
\beta_6 &\sim \text{Normal}(0, 2.5)
\end{align}

where binary variable $vote\_harris_i$ is equal to 1 if the respondent's preferred 2024 presidential candidate is Kamala Harris, or 0 if the respondent's preferred 2024 presidential candidate is Donald Trump. We run our model in R [@citeR] using `stan_glm`, with the default priors from `rstanarm` [@citerstanarm]. We then apply our model to our post-stratification data [@citeIPUMS] to predict the popular vote and electoral college results of the 2024 U.S. Presidential election.

@@

# Appendix {-}

@@

# Appendix
## Emerson College Polling Methodology
For this deep dive, I'll focus on Emerson College Polling based on the link: Emerson College Polling - October 2024 National Poll.
Survey Overview:
The Emerson College Polling conducted a national survey in October 2024 to assess voter preferences for the upcoming U.S. presidential election. This appendix provides an in-depth analysis of their polling methodology, including the population, sample frame, recruitment process, and key strengths and weaknesses of their approach.

@@

## Idealized Methodology for US Presidential Election Forecast
This appendix outlines the methodology and design for conducting a U.S. presidential election forecast survey with a budget of $100,000. The goal is to develop an accurate and reliable prediction of the election outcome, ensuring data quality through careful sampling, recruitment, validation, and aggregation of results.

Methodology Overview
1. Sampling Approach
To ensure a representative sample of likely voters, I will use a stratified random sampling method based on demographic and voter turnout data from the U.S. Census and previous elections.

Target Population: U.S. citizens eligible to vote in the 2024 U.S. presidential election.
Sample Size: I plan to survey 3,500 respondents, providing a margin of error of approximately ±1.7 percentage points, ensuring a high level of confidence in the results.
Stratification Variables: The sample will be stratified by age, gender, race/ethnicity, education level, geographic region, and income. This ensures that each demographic group is represented proportionally to the U.S. population.
Oversampling: To ensure insights into underrepresented or low-response groups (e.g., younger voters, minorities), I will oversample these groups and apply appropriate post-stratification weighting.
2. Recruitment of Respondents
I will use a multi-modal approach to recruit a diverse and representative sample, employing both online and offline strategies to reach various segments of the population.

@@

5. Questionnaire Design
The survey will be structured to capture key insights into voting intention, candidate favorability, and the issues driving voter decisions. It will be short and simple, taking no more than 10 minutes to complete.
Survey Link
The survey has been implemented using Google Forms. Here is the link to access the survey:\
https://docs.google.com/forms/d/e/1FAIpQLSetY5pPLMYHn4YXF2uIxVNnCGUB1PRvyHbSd3HF3E6DdN2EkA/viewform

Budget Breakdown
Here is a proposed allocation of the $100,000 budget:\
Survey Platform and Software Costs: $5,000 for survey hosting on Google Forms and Qualtrics.
Recruitment Costs: $40,000 for online panel recruitment, social media ads, and targeted outreach.
Phone and SMS Polling: $20,000 to cover live phone interviews and SMS polling.
Fieldwork in Key States: $15,000 for in-person recruitment in battleground states.
Data Validation and Cleaning: $10,000 for voter verification, attention checks, and cleaning services.
Poll Aggregation and Modeling Tools: $7,000 for the development of a poll aggregation tool and Bayesian forecasting model.
Miscellaneous Costs: $3,000 for administrative costs, project management, and reporting.

>>>>

In addition to constructing and interpreting predictive models, this paper dive into the methods used by xx pollsters, analyzing the strengths as well as the weaknesses of the methods used against them. At the end of the paper, we also propose an idealized survey methodology for election forecasting with a budget of \$100,000 USD.

@@

```{=tex}
\begin{align} 
vote\_harris_i|\pi_i &\sim \text{Bernoulli}(\pi_i) \\
\text{logit}(\pi_i) &= \beta_0 + \beta_1 \text{sex}_i + \beta_2  \text{age\_bracket}_i + \beta_3 \text{race}_i + \beta_4 \text{race\_hispanic}_i + \beta_5 \text{education\_level}_i + \beta_6 \text{urban}_i \\
\beta_0 &\sim \text{Normal}(0, 2.5) \\
\beta_1 &\sim \text{Normal}(0, 2.5) \\
\beta_2 &\sim \text{Normal}(0, 2.5) \\
\beta_3 &\sim \text{Normal}(0, 2.5) \\
\beta_4 &\sim \text{Normal}(0, 2.5) \\
\beta_5 &\sim \text{Normal}(0, 2.5) \\
\beta_6 &\sim \text{Normal}(0, 2.5)
\end{align}
```
where binary variable $vote\_harris_i$ is equal to 1 if the respondent's preferred 2024 presidential candidate is Kamala Harris, or 0 if the respondent's preferred 2024 presidential candidate is Donald Trump. We run our model in R [@citeR] using `stan_glm`, with the default priors from `rstanarm` [@citerstanarm]. We then apply our model to our post-stratification data [@citeIPUMS] to predict the popular vote and electoral college results of the 2024 U.S. Presidential election.

@@

# Appendix {.unnumbered}

@@

# Appendix

## Emerson College Polling Methodology

For this deep dive, I'll focus on Emerson College Polling based on the link: Emerson College Polling - October 2024 National Poll. Survey Overview: The Emerson College Polling conducted a national survey in October 2024 to assess voter preferences for the upcoming U.S. presidential election. This appendix provides an in-depth analysis of their polling methodology, including the population, sample frame, recruitment process, and key strengths and weaknesses of their approach.

@@

## Idealized Methodology for US Presidential Election Forecast

This appendix outlines the methodology and design for conducting a U.S. presidential election forecast survey with a budget of \$100,000. The goal is to develop an accurate and reliable prediction of the election outcome, ensuring data quality through careful sampling, recruitment, validation, and aggregation of results.\

### Methodology

#### Sampling Approach

To ensure a representative sample of likely voters, I will use a Composite Measure sampling method based on the past voter turnout data from the U.S. previous 2020 elections.After decising the sampling size in each state, I will use a stratified sampling bases on demographics,dividing population into subgroups, and a random sample is taken from each subgroup. We employ composite Measure sampling method refer from (), that increased our chances of selecting respondents from voters in states/ regions that have historically higher voter engagement as compared to the natural distribution we’d expect from the general population. While some states may have larger populations, we are interested in adjusting the sampling to reflect higher turnout rates. To better explain this composite measure of size, lets consider that we have two states that have similar population. For example, even though State A and State B may have similar populations, if State B consistently has a higher voter turnout in past elections, we want to increase the proportion of polls we conduct in State B. State A has a population of 1 million eligible voters, with a historical turnout rate of 50%. State B has a population of 1 million eligible voters, but its turnout rate is 70%. In a purely population-based sampling approach, each state would have an equal chance of being selected for polls: 50% for State A and 50% for State B. However, based on voter turnout, we modify these probabilities to increase the chance of selecting State B, since its voter turnout is historically higher.\
In following steps, we will explore how to use **voter turnout** as a key factor to create a **composite measure of size** for sampling US election polls. Instead of using population size alone, we adjust the sample allocation based on historical voter turnout, ensuring regions with higher engagement are more heavily represented in our polling data.\

##### Step 1: Define the Sampling Data

We begin by collecting the **eligible voter population** and **historical voter turnout rates** for different states. In this simplified example, we will focus on two states: **State A** and **State B**.

| State   | Eligible Voters | Turnout Rate |
|---------|-----------------|--------------|
| State A | 1,000,000       | 50%          |
| State B | 1,000,000       | 70%          |

##### Step 2: Calculate Actual Voters

Next, we calculate the **number of actual voters** in each state by multiplying the eligible voters by the turnout rate: $$\text{Actual Voters} = \text{Eligible Voters} \times \text{Turnout Rate}$$\
Actual voters in State A: $\text{Actual Voters}_A = 1,000,000 \times 0.50 = 500,000$\
Actual voters in State B: $\text{Actual Voters}_B = 1,000,000 \times 0.70 = 700,000$\
Total actual voters: $\text{Actual Voters}_A+\text{Actual Voters}_B= 500,000 + 700,000 = 1,200,000$\

##### Step 3: Calculate Composite Measure of Size

We now calculate the **total number of voters** across both states and determine the **proportion** of each state's turnout relative to the total. This forms the basis of the composite measure of size, which we will use to adjust the sampling weights.

The total voters in two states are 1,200,000. Therefore, the sampling proportion for State A is: $\text{Sampling Proportion}_A = \frac{500,000}{1,200,000} \approx 0.417$, and for State B is: $\text{Sampling Proportion}_B = \frac{700,000}{1,200,000} \approx 0.583$

##### Step 4: Allocate Sample Based on Turnout

Finally, we allocate the sample size according to the calculated sampling proportions. For instance, if we are conducting 1,000 polls, we would allocate State A with $\text{Polls for State A} = 1,000 \times 0.417 \approx 417 \text{polls}$ and State B with $\text{Polls for State B} = 1,000 \times 0.583 \approx 583 \text{polls}$

By using historical voter turnout to adjust our polling sample, we ensure that regions with higher voter engagement have a greater influence on the polling results. This composite measure of size ensures that our polling sample better reflects the actual voting patterns and preferences in different regions. Consequently, we can produce more accurate and representative poll outcomes that account for the varying levels of voter participation across the country.

### Target Population

Our target population is all U.S. citizens eligible to vote in the 2024 U.S. presidential election (age\>=18).

### Sample frame

### Sample

#### Sample Size:

We plan to survey 300 respondents, which will provide a margin of error of approximately ±1.7 percentage points, ensuring a high level of confidence in the results. Given the limited sample size and to enhance the effectiveness of stratified sampling, the states will be grouped into four regions: Midwest, Northeast, South, and West. The sample size for each region will be allocated based on the proportion of total ballots cast in each region during the 2020 election. The regional grouping of states is shown in @tbl-region.

| **Region**    | **States**                                                                                                                                                 |
|------------------------------------|------------------------------------|
| **MIDWEST**   | Illinois, Indiana, Iowa, Kansas, Michigan, Minnesota, Missouri, Nebraska, North Dakota, Ohio, South Dakota, Wisconsin                                      |
| **Northeast** | Connecticut, Delaware, District of Columbia, Maine, Maryland, Massachusetts, New Hampshire, New Jersey, New York, Pennsylvania, Rhode Island, Vermont      |
| **SOUTH**     | Alabama, Arkansas, Florida, Georgia, Kentucky, Louisiana, Mississippi, North Carolina, Oklahoma, South Carolina, Tennessee, Texas, Virginia, West Virginia |
| **WEST**      | Alaska, Arizona, California, Colorado, Hawaii, Idaho, Montana, Nevada, New Mexico, Oregon, Utah, Washington, Wyoming                                       |

: Regional Grouping of States in the USA {#tbl-region}

| **Region**  | **Voter Turnout (%)** | **Total Ballots Cast** | **VEP**    | **Composite Measure Sampling Proportion** | **Sample Size** |
|-----------|-----------|-----------|-----------|-----------------|-----------|
| **MIDWEST** | 69%                   | 35,134,960             | 50,932,439 | 0.214805579                               | 64              |
| **NW**      | 68%                   | 32,262,303             | 47,473,317 | 0.200216867                               | 60              |
| **SOUTH**   | 65%                   | 54,746,770             | 84,563,831 | 0.356644666                               | 107             |
| **WEST**    | 69%                   | 37,594,304             | 54,139,892 | 0.228332888                               | 68              |

: Regional Voting Data and Sample Size Allocation Based on 2020 Election Turnout{#tbl-sample_size}

@tbl-sample_size shows the regional breakdown of the 2020 election data, sourced from [@wiki], including voter turnout, total ballots cast, and Voting Eligible Population (VEP). The sample size for each region was determined based on the **Composite Measure Sampling Proportion**.

Stratification Variables: The sample will be stratified by age, gender, race/ethnicity, education level, geographic region, and income. This ensures that each demographic group is represented proportionally to the U.S. population.

Oversampling: To ensure insights into underrepresented or low-response groups (e.g., younger voters, minorities), I will oversample these groups and apply appropriate post-stratification weighting.

#### Recruitment of Respondents

I will use a multi-modal approach to recruit a diverse and representative sample, employing both online and offline strategies to reach various segments of the population.

@@

5.  Questionnaire Design The survey will be structured to capture key insights into voting intention, candidate favorability, and the issues driving voter decisions. It will be short and simple, taking no more than 10 minutes to complete. Survey Link The survey has been implemented using Google Forms. Here is the link to access the survey:\
    https://forms.gle/BAZhkWDyLxAibwvu5

Budget Breakdown Here is a proposed allocation of the \$100,000 budget:\
Survey Platform and Software Costs: \$5,000 for survey hosting on Google Forms and Qualtrics. Recruitment Costs: \$40,000 for online panel recruitment, social media ads, and targeted outreach. Phone and SMS Polling: \$20,000 to cover live phone interviews and SMS polling. Fieldwork in Key States: \$15,000 for in-person recruitment in battleground states. Data Validation and Cleaning: \$10,000 for voter verification, attention checks, and cleaning services. Poll Aggregation and Modeling Tools: \$7,000 for the development of a poll aggregation tool and Bayesian forecasting model. Miscellaneous Costs: \$3,000 for administrative costs, project management, and reporting.
